Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-08-01 literature/paper_draft.qmd
mention reconcov :)

@@

>>>>

All data generation, covariance estimation, and reconciliation routines were implemented in the ReconCov R package, a package developed solely for this research, and is available under an open‐source license on GitHub [@ReconCov].

@@

The cross-validation algorithm for NOVELIST is available in the ReconCov package [@ReconCov].
